Case Study (McKenna)

### 2021-02-17 Cases/mrp/Case Study (McKenna) .Rmd
edit messages

## Model

```{r load-data, message=FALSE}
library(tidyverse) #Load packages
library(rstan)
library(rstanarm)
library(ggplot2)
library(bayesplot)
theme_set(bayesplot::theme_default())
library(dplyr)
library(tidyr)
library(tidybayes)
library(here)
```

```{r}
simulate_mrp_data <- function(n) {
  J <- c(2, 3, 7) # male or not, eth, age
  # poststrat <- as.data.frame(array(NA, c(prod(J), length(J)+1))) 
  poststrat <- as.data.frame(array(NA, c(prod(J), length(J)))) 
  # Columns of post-strat matrix, plus one for size
  colnames(poststrat) <- c("male", "eth", "age")
  count <- 0
  for (i1 in 1:J[1]){
    for (i2 in 1:J[2]){
      for (i3 in 1:J[3]){
            count <- count + 1
            # Fill them in so we know what category we are referring to
            poststrat[count, 1:3] <- c(i1-1, i2, i3)
          }
        }
      }
  # Proportion in each sample in the population
  p_male <- c(0.52, 0.48)
  p_eth <- c(0.2, 0.3, 0.5)
  p_age <- c(0.1, 0.1, 0.2, 0.2, 0.1, 0.1, 0.2)
  poststrat$N<-0
  for (j in 1:prod(J)){
    poststrat$N[j] <- round(250e6 * p_male[poststrat[j,1]+1] * p_eth[poststrat[j,2]] *
                              p_age[poststrat[j,3]]) 
    #Adjust the N to be the number observed in each category in each group
  }
  # Now let's adjust for the probability of response
  p_response_baseline <- 0.01
  p_response_male <- c(2, 0.8) / 2.8
  p_response_eth <- c(1, 1.2, 2.5) / 4.7
  p_response_age <- c(1, 0.4, 1, 1.5,  3, 5, 7) / 18.9
  p_response <- rep(NA, prod(J))
  for (j in 1:prod(J)) {
    p_response[j] <-
      p_response_baseline * p_response_male[poststrat[j, 1] + 1] *
      p_response_eth[poststrat[j, 2]] * p_response_age[poststrat[j, 3]]
  }
  people <- sample(prod(J), n, replace = TRUE, prob = poststrat$N * p_response)
  ## For respondent i, people[i] is that person's poststrat cell,
  ## some number between 1 and 32
  n_cell <- rep(NA, prod(J))
  for (j in 1:prod(J)) {
    n_cell[j] <- sum(people == j)
  }
  coef_male <- c(0,-0.3)
  coef_eth <- c(0, 0.6, 0.9)
  coef_age <- c(0,-0.2,-0.3, 0.4, 0.5, 0.7, 0.8, 0.9)
  coef_age_male <- t(cbind(c(0, .1, .23, .3, .43, .5, .6),
                           c(0, -.1, -.23, -.5, -.43, -.5, -.6)))
  true_popn <- data.frame(poststrat[, 1:3], service_failure = rep(NA, prod(J)))
  for (j in 1:prod(J)) {
    true_popn$satisfaction[j] <- plogis(
      coef_male[poststrat[j, 1] + 1] +
        coef_eth[poststrat[j, 2]] + coef_age[poststrat[j, 3]] +
        coef_age_male[poststrat[j, 1] + 1, poststrat[j, 3]]
    )
  }
  #male or not, eth, age
  y <- rbinom(n, 1, true_popn$satisfaction[people])
  male <- poststrat[people, 1]
  eth <- poststrat[people, 2]
  age <- poststrat[people, 3]
  sample <- data.frame(service_failure = y,
                       male, age, eth,
                       id = 1:length(people))
  #Make all numeric:
  for (i in 1:ncol(poststrat)) {
    poststrat[, i] <- as.numeric(poststrat[, i])
  }
  for (i in 1:ncol(true_popn)) {
    true_popn[, i] <- as.numeric(true_popn[, i])
  }
  for (i in 1:ncol(sample)) {
    sample[, i] <- as.numeric(sample[, i])
  }
  list(
    sample = sample,
    poststrat = poststrat,
    true_popn = true_popn
  )
}
mrp_sim <- simulate_mrp_data(n=1200)
sample <- mrp_sim[["sample"]]
poststrat <- mrp_sim[["poststrat"]]
true_popn <- mrp_sim[["true_popn"]]
```

@@

```{r, eval = FALSE}
fit <- stan(
  file = here::here("Code", "mrp", "logit_hier.stan"),
  data = data_list,
  seed = 42 
)
```

>>>>

## Model
# Here we are loading the packages needed to run our model

```{r load-data, message=FALSE}
library(tidyverse) #Load packages
library(rstan)
library(rstanarm)
library(ggplot2)
library(bayesplot)
theme_set(bayesplot::theme_default())
library(dplyr)
library(tidyr)
library(tidybayes)
library(here)
options(mc.cores = parallel::detectCores())
```

```{r}
simulate_mrp_data <- function(n) {
  J <- c(2, 3, 7) # male or not, eth, age
  # poststrat <- as.data.frame(array(NA, c(prod(J), length(J)+1))) 
  poststrat <- as.data.frame(array(NA, c(prod(J), length(J)))) 
  # Columns of post-strat matrix with the various variables that we will be using
  colnames(poststrat) <- c("male", "eth", "age")
  count <- 0
  for (i1 in 1:J[1]){
    for (i2 in 1:J[2]){
      for (i3 in 1:J[3]){
            count <- count + 1
            # Fill them in so we know what category we are referring to
            poststrat[count, 1:3] <- c(i1-1, i2, i3)
          }
        }
      }
  # Proportion in each sample in the population, we cut down the proportions in this, you can adjust them based on how many you would like in each category
  p_male <- c(0.52, 0.48)
  p_eth <- c(0.2, 0.3, 0.5)
  p_age <- c(0.1, 0.1, 0.2, 0.2, 0.1, 0.1, 0.2)
  poststrat$N<-0
  for (j in 1:prod(J)){
    poststrat$N[j] <- round(250e6 * p_male[poststrat[j,1]+1] * p_eth[poststrat[j,2]] *
                              p_age[poststrat[j,3]]) 
    #Adjust the N to be the number observed in each category in each group
  }
  # Now let's adjust for the probability of response
  p_response_baseline <- 0.01
  p_response_male <- c(2, 0.8) / 2.8
  p_response_eth <- c(1, 1.2, 2.5) / 4.7
  p_response_age <- c(1, 0.4, 1, 1.5,  3, 5, 7) / 18.9
  p_response <- rep(NA, prod(J))
  for (j in 1:prod(J)) {
    p_response[j] <-
      p_response_baseline * p_response_male[poststrat[j, 1] + 1] *
      p_response_eth[poststrat[j, 2]] * p_response_age[poststrat[j, 3]]
  }
  people <- sample(prod(J), n, replace = TRUE, prob = poststrat$N * p_response)
  ## For respondent i, people[i] is that person's poststrat cell,
  ## some number between 1 and 32
  n_cell <- rep(NA, prod(J))
  for (j in 1:prod(J)) {
    n_cell[j] <- sum(people == j)
  }
  coef_male <- c(0,-0.3)
  coef_eth <- c(0, 0.6, 0.9)
  coef_age <- c(0,-0.2,-0.3, 0.4, 0.5, 0.7, 0.8, 0.9)
  coef_age_male <- t(cbind(c(0, .1, .23, .3, .43, .5, .6),
                           c(0, -.1, -.23, -.5, -.43, -.5, -.6)))
  true_popn <- data.frame(poststrat[, 1:3], service_failure = rep(NA, prod(J)))
  for (j in 1:prod(J)) {
    true_popn$satisfaction[j] <- plogis(
      coef_male[poststrat[j, 1] + 1] +
        coef_eth[poststrat[j, 2]] + coef_age[poststrat[j, 3]] +
        coef_age_male[poststrat[j, 1] + 1, poststrat[j, 3]]
    )
  }
  #male or not, eth, age
  y <- rbinom(n, 1, true_popn$satisfaction[people])
  male <- poststrat[people, 1]
  eth <- poststrat[people, 2]
  age <- poststrat[people, 3]
  sample <- data.frame(service_failure = y,
                       male, age, eth,
                       id = 1:length(people))
  #Make all numeric:
  for (i in 1:ncol(poststrat)) {
    poststrat[, i] <- as.numeric(poststrat[, i])
  }
  for (i in 1:ncol(true_popn)) {
    true_popn[, i] <- as.numeric(true_popn[, i])
  }
  for (i in 1:ncol(sample)) {
    sample[, i] <- as.numeric(sample[, i])
  }
  list(
    sample = sample,
    poststrat = poststrat,
    true_popn = true_popn
  )
}
mrp_sim <- simulate_mrp_data(n=1200)
sample <- mrp_sim[["sample"]]
poststrat <- mrp_sim[["poststrat"]]
true_popn <- mrp_sim[["true_popn"]]
```

@@

```{r, eval = FALSE}
fit <- stan(
  file = here::here("Code", "mrp", "logit_hier.stan"),
  data = data_list,
  iter = 2000,
  thin = 2,
  seed = 42 
)
```
